Meta-analysis of composite outcomes in clinical trials

### 2025-01-28 MSc_poster_template.Rmd
Minor adjustments

# Background and Problem
Composites are commonly used in clinical trials as the primary outcome. When misused, they can reduce the power to detect treatment effect. This was seen in EMERGE [^1], a randomised clinical trial investigating the effects of early initiation of Metformin treatment on developing gestational diabetes. The composite was created using three measures of glycemic control; blood glucose levels of 5.1mmol/L or greater at gestation weeks 32 or 38, or initiation of Insulin treatment.

@@

This composite involves dichotomising blood glucose levels, greatly reducing power. Therefore, the objectives of this project are:

1.	To perform a meta-analysis of the primary outcome using permutations of the composite test statistic, and analyzing the glucose components as continuous variables

>>>>

# Background and Problem
Composites are commonly used in clinical trials as the primary outcome. When misused, they can reduce the power to detect treatment effect. This was seen in EMERGE, [^1] a randomised clinical trial investigating the effects of early initiation of Metformin treatment on developing gestational diabetes. The composite was created using three measures of glycemic control; blood glucose levels of 5.1mmol/L or greater at gestation weeks 32 or 38, or initiation of Insulin treatment.

@@

This composite involves dichotomising blood glucose levels, greatly reducing power. Therefore, using data from EMERGE, the objectives of this project are:

1.	To perform a meta-analysis of the primary outcome using permutations of the composite test statistic, without dichotomising glucose variables
